Comparing to lognormal, Poisson, exponential

### 2021-03-08 analysis/rev_prototyping/ct.Rmd
helps if you return the output

po_central_tendency <- function(fs_df, fs_po_df) {

  ct_sim <- dplyr::filter(fs_po_df, mean_po_comparison == min(fs_po_df$mean_po_comparison))$focal_sim[1]

  ct_pos <- compare_props_off_full(ct_sim, fs_df, ncomps = length(unique(fs_df$sim)) - 2) %>%
    dplyr::distinct()

  real_po <- proportion_off(t(data.frame(dplyr::filter(fs_df, source == "observed")$abund, dplyr::filter(fs_df, sim == ct_sim)$abund)))

  out <- fs_df %>%
    dplyr::filter(source == "observed") %>%
    dplyr::select(source, dat, site, singletons, s0, n0, sim, nparts) %>%
    dplyr::distinct() %>%
    dplyr::mutate(
      real_po = real_po,
      best_po_sim = ct_sim,
      sim_devs_from_best = mean(ct_pos$prop_off),
      ncomparisons = nrow(ct_pos),
      real_po_percentile = get_percentile(real_po, ct_pos$prop_off),
      real_po_percentile_excl = get_percentile(real_po, ct_pos$prop_off, incl = F)
    )

}

>>>>

```{r}
# 
# po_central_tendency <- function(fs_df, fs_po_df) {
#   
#   ct_sim <- dplyr::filter(fs_po_df, mean_po_comparison == min(fs_po_df$mean_po_comparison))$focal_sim[1]
#   
#   ct_pos <- compare_props_off_full(ct_sim, fs_df, ncomps = length(unique(fs_df$sim)) - 2) %>%
#     dplyr::distinct()
#   
#   real_po <- proportion_off(t(data.frame(dplyr::filter(fs_df, source == "observed")$abund, dplyr::filter(fs_df, sim == ct_sim)$abund)))
# 
#   out <- fs_df %>%
#     dplyr::filter(source == "observed") %>%
#     dplyr::select(source, dat, site, singletons, s0, n0, sim, nparts) %>%
#     dplyr::distinct() %>%
#     dplyr::mutate(
#       real_po = real_po,
#       best_po_sim = ct_sim,
#       sim_devs_from_best = mean(ct_pos$prop_off),
#       ncomparisons = nrow(ct_pos),
#       real_po_percentile = get_percentile(real_po, ct_pos$prop_off),
#       real_po_percentile_excl = get_percentile(real_po, ct_pos$prop_off, incl = F)
#     )
# 
# }

po_central_tendency(fs, fs_pc)
